\textbf{How to measure maximally precise radial velocities from a set of spectra:\\ The time-independent spectrum case}

### 2019-08-15 paper/eprv.tex
abstract tweaks

\begin{abstract}\noindent
% context
Extremely precise stellar radial velocity (\RV) measurements
have been used to to discover hundreds of exoplanets, and
many new spectrographs are being built for exoplanet search and
characterization.
Current observations are delivering \RV\ measurements at $\mps$
precision.
It appears that many hardware systems ought to be---on the basis of
both spectrograph-stability and information-theoretic
considerations---capable of delivering even higher precisions.
% aims
Here we ask: What data-analysis methods deliver \RV\ measurements that
saturate the Cram\'er--Rao bound (\CRLB) on precision, given an
extracted spectrum (and associated uncertainties) from a spectrograph?
We presume that the stellar spectrum does not vary with time (this is
incorrect in detail).
% methods
We consider a smoothed (or
Gaussian-fit) cross-correlation with a binary mask,
cross-correlation with a stellar template,
and maximum-likelihood methods.
We draw out the relationships between these.
We consider both theoretically generated and data-driven templates.
% results
We find (as expected) that cross-correlation with a correct stellar
template produces \RV\ measurements that saturate the \CRLB.
We also find that 
the currently standard practice of fitting a Gaussian to the cross-correlation
with a binary mask saturates the \CRLB, so long as the binary mask is
correct in a certain sense.
As the template or mask becomes incorrect, \RV\ precision suffers.
Un-corrected telluric absorption lines can also harm \RV\ precision.
Most importantly, we find that using the data themselves to generate
the stellar and telluric templates does not cost any significant
information, once the number of observational epochs is large.
That is, data-driven stellar and telluric templates can be correct
enough to saturate the \CRLB, provided that
the star does not vary substantially between epochs.
If the star does vary substantially, a lot more needs to be known
before the relevant \CRLB\ even can be computed.
\end{abstract}

@@

\section{Introduction}

>>>>

\begin{abstract}\noindent
% context
Extremely precise stellar radial velocity (\RV) measurements
have been used to discover hundreds of exoplanets, and
many new spectrographs are being built for exoplanet search and
characterization.
The best published results show empirical precision at the $\mps$ level.
Information theory suggests that it ought to be possible ot reach
higher precisions with current observations.
% aims
Here we ask: What data-analysis methods deliver \RV\ measurements that
saturate the Cram\'er--Rao bound (\CRLB) on precision, given an
extracted spectrum (and associated uncertainties) from a spectrograph?
We presume that the stellar spectrum does not vary with time (this is
incorrect in detail).
% methods
We consider a smoothed (or
Gaussian-fit) cross-correlation with a binary mask,
cross-correlation with a stellar template,
and maximum-likelihood methods.
We draw out the relationships between these.
We consider both theoretically generated and data-driven templates.
% results
We find (as expected) that cross-correlation with a correct stellar
template produces \RV\ measurements that saturate the \CRLB.
We also find that 
the standard practice of fitting a Gaussian to the cross-correlation
with a binary mask saturates the \CRLB, so long as the binary mask is
correct in a certain sense.
As the template or mask becomes incorrect, \RV\ precision suffers.
Un-corrected telluric absorption lines can also harm \RV\ precision.
Most importantly, we find that using the data themselves to generate
the stellar and telluric templates does not cost any significant
information, once the number of observational epochs is large.
That is, data-driven stellar and telluric templates can be used to
saturate the \CRLB, provided that
the star does not vary substantially between epochs.
If the star does vary substantially, a lot more needs to be known
before the relevant \CRLB\ even can be computed.
\end{abstract}

@@

\clearpage
\section{Introduction}
